### 2020-09-08 ART_Czarnik/Czarnik-PU.tex
Authors' and editorial corrections added

\begin{table}[H]
\begin{flushleft}
\begin{small}
\begin{tabular}{|m{.19\textwidth}|m{.22\textwidth}|m{.13\textwidth}|m{.3\textwidth}|}
\hline
\centering{\bfseries Type} &
\centering{\bfseries Specification} &
\centering{\bfseries Example} &
\centering\arraybackslash{\bfseries Epistemic consequence(s)}\\\hline
monotomous\footnotemark

(one-to-none) &
focuses on a single group, no comparison to other groups is implied &
Catholics don't eat meat on Fridays. &
We assume to know the trait prevalence/intensity in the group.\\\hline
dichotomous

(one-to-one) &
there are two relevant groups, one is compared to the other &
Women are more law-abiding than men. &
We assume to know the relative prevalence/intensity of the trait in both groups. \\\hline
polytomous

(one-to-many) &
there are many relevant groups, one is singled out for inspection &
Poles make brave soldiers. &
We assume to know that the prevalence/intensity of the trait in the focal group is above average.

We don't necessarily assume to know anything about any other group in particular. \\\hline
incremental &
groups are implicitly defined and ordered by intensity of certain characteristic &
The older, the more clumsy. &
We assume to know that prevalence/intensity of the trait is monotonously linked to the group-defining metric.\\\hline

@@

\begin{enumerate}
\item
  \(\mu_{T} = 2.00\) and \(\sigma_{T} = 0.75\), with the corresponding
  \(p\left( X_{T} > X_{R} \right) = 0.945\);
\item
  \(\mu_{T} = 1.00\) and \(\sigma_{T} = 1.00\), with the corresponding
  \(p\left( X_{T} > X_{R} \right) = 0.760\);
\item
  \(\mu_{T} = 0.25\) and \(\sigma_{T} = 1.50\), with the corresponding
  \(p\left( X_{T} > X_{R} \right) = 0.555\).
\end{enumerate}
In A, the stereotype could be considered to be very accurate as it would produce mistakes when judging individuals only 5.5\% of the time. In C, it is barely acceptable, with failure rate at 44.5\%. What about B? With the error rate at 24\% it seems quite unreliable. But before discarding it as a far-fetched overgeneralization, one should recognize that according to a popular metric proposed by
%\label{ref:RNDI9cG7tk2qD}(Cohen, 1988),
\parencite[][]{cohen_statistical_1988}, %
 this stereotype signifies a definitely large effect size. With Cohen's \textit{d} equal to 1, it is the kind of effect that any social scientist would be more than happy to find in his or her study. Moreover, let us bear in mind that for ``new areas of research inquiry,'' effect sizes of 0.2 would not be utterly uninteresting 
%\label{ref:RNDDeitIcl8zR}(Cohen, 1988, p.25).
\parencite[][p.25]{cohen_statistical_1988}. %
 And it is just the effect size of a stereotypic difference depicted by C. Why should we then subject stereotypes to higher standards of truth than scientific findings?

@@

\setlength{\tabcolsep}{2pt}
\begin{figure}[H]
	\begin{small}
   \begin{supertabular}{m{.32\textwidth}m{.32\textwidth}m{.32\textwidth}}
   \begin{center}
   \textbf{moderate effect size}
   \end{center} &
   \begin{center}
   \textbf{large effect size}
   \end{center} &
   \begin{center}
   \textbf{very large effect size}
   \end{center} \\
	\vskip-.3in$$\mu_{T} - \mu_{R} = 0.5$$\vskip-.3in &
    \vskip-.3in$$\mu_{T} - \mu_{R} = 1.0$$\vskip-.3in &
    \vskip-.3in$$\mu_{T} - \mu_{R} = 1.5$$\vskip-.3in \\
   \includegraphics[width=\linewidth]{ART_Czarnik/Czarnik-img016.jpg} &
   \includegraphics[width=\linewidth]{ART_Czarnik/Czarnik-img017.jpg} &
   \includegraphics[width=\linewidth]{ART_Czarnik/Czarnik-img018.jpg} \\
   \end{supertabular}
   \end{small}
\caption{The effect of categorization on the observed
probabilities of \(X_{T} > X_{R}\), \(X_{T} = X_{R}\), and
\(X_{T} < X_{R}\) for three different effect sizes (all underlying
distributions are normal with \(\sigma_{T} = \sigma_{R} = 1\)).}\label{fig2-czar}
\end{figure}
When analyzing the accuracy of stereotypes regarding traits measured on
scales with a limited number of categories it is thus advisable to
consider all three possible options: \(X_{T} > X_{R}\),
\(X_{T} = X_{R}\), and \(X_{T} < X_{R}\), as it may well turn out that
\(p\left( X_{T} = X_{R} \right)\) is far from negligible.

\section{A few empirical examples of assessing the accuracy of sex stereotypes}
\enlargethispage{-2\baselineskip}
Both actual differences between the sexes and associated beliefs about these differences were intensively studied
%\label{ref:RND1zeV4PeuSF}(Williams and Best, 1982, 1990; Costa, Terracciano and McCrae, 2001; Biernat and Deaux, 2000; Buss, 2003; Pinker, 2003).
\parencites[][]{williams_measuring_1982}[][]{williams_sex_1990}[][]{costa_gender_2001}[][]{borgatta_sex_2000}[][]{buss_evolution_2003}[][]{pinker_blank_2003}. %
 In the following, I~will examine a number of possible sex stereotypes, testing their accuracy against the survey data from Polish General Social Survey 
%\label{ref:RNDDqAxDLuyEC}(Cichomski, Jerzyński and Zieliński., 2013)
\parencite[][]{cichomski_polskie_2013} %
 and the Study of Human Capital in Poland 
%\label{ref:RNDLH293GzyiT}(Górniak et al., 2015, 2019).
\parencites[][]{gorniak_bilans_2015}[][]{gorniak_bilans_2019}.%
\footnote{Representative surveys provide us with proper criteria for assessing stereotypes' accuracy. } It is irrelevant here whether most people (or any people, for that matter) subscribe to these particular stereotypes, although certainly some of the inspected traits are popularly held to be gender-differentiating (e.g. body height, earnings, interest in fashion or technology).

For each trait, probabilities of a randomly selected woman being at a
higher, the same, or lower level on the trait as compared to a randomly
selected man were computed, using the following formulae, where \emph{v}
stands for a value of the trait variable\footnote{It may be noted that a
  difference between the ``mirror-image'' probabilities, i.e.
  \(p\left( X_{F} > X_{M} \right) - p\left( X_{F} < X_{M} \right)\)\emph{,
  is equal in value to asymmetric Somer's d rank correlation coefficient
  (Somers, 1962), when predictions are based on subjects' sex.}}:
\[p\left( X_{F} > X_{M} \right) = \sum_{v = min}^{\max}{p\left( X_{F} = v \right) \bullet p\left( X_{M} < v \right)}\]

\[p\left( X_{F} = X_{M} \right) = \sum_{v = min}^{\max}{p\left( X_{F} = v \right) \bullet p\left( X_{M} = v \right)}\]

\[p\left( X_{F} < X_{M} \right) = \sum_{v = min}^{\max}{p\left( X_{F} = v \right) \bullet p\left( X_{M} > v \right)}\]

@@

\begin{figure}[H]
	\centering
   \includegraphics[width=\textwidth]{ART_Czarnik/Czarnik-img019.jpg}
\caption{Probabilistic assessment of stereotypical sex differences concerning body structure Polish General Social Survey. Open-ended questions (``What is your height and weight, approximately?'').}\label{fig3-czar}
\end{figure}

@@

\begin{figure}[H]
	\centering
   \includegraphics[width=\textwidth]{ART_Czarnik/Czarnik-img020.jpg}
\caption{Probabilistic assessment of stereotypical sex differences concerning pay* Study of Human Capital in Poland. Open-ended question with supplementary categorization. \\ * Data for employees with job contracts working full-time within last month, excluding the self-employed.}\label{fig4-czar}
\end{figure}

@@

\begin{figure}[H]
	\centering
   \includegraphics[width=\textwidth]{ART_Czarnik/Czarnik-img021.jpg}
\caption{Probabilistic assessment of stereotypical sex differences concerning interest in the mass media content Polish General Social Survey (2002). Interest measured on a 4-point scale: 1 not at all /2 not much /3 quite a bit /4 very much.}\label{fig5-czar}
\end{figure}

@@

\begin{figure}[h]
	\centering
   \includegraphics[width=\textwidth]{ART_Czarnik/Czarnik-img022.jpg}
\caption{Probabilistic assessment of stereotypical sex differences concerning skill self-evaluation Study of Human Capital in Poland (2017). Skill level self-valuated on a 5-point scale: 1 low /2 basic /3 medium /4 high /5 very high.}\label{fig6-czar}
\end{figure}

@@

\myquote{
Imagine that you enter an elevator in a large shopping mall and two random persons—one man and one woman—unknown to you and to each other,\footnote{It is important to exclude the possibility that a man and a woman are a couple, so that subjects' judgment about general differences would not be contaminated by their beliefs about relative height of mated individuals. } enter after you. How likely it is that: (1) the man will be the taller of the two, (2) the woman will be the taller of the two, (3) they will be of equal height (with precision of, say, 1 cm). Make sure that probabilities add to 100\%.\footnote{It is a subject for some experimentation to find out how this task could be facilitated by a particular method of registering the probabilities (e.g. by a visual representation of probabilities on screen). }
}

>>>>

\begin{table}[H]
\begin{flushleft}
\begin{small}
%\begin{tabular}{|m{.19\textwidth}|m{.22\textwidth}|m{.13\textwidth}|m{.3\textwidth}|}
\begin{tabular}{|L{.19\textwidth}|L{.22\textwidth}|L{.13\textwidth}|L{.28\textwidth}|}
\hline
\multicolumn{1}{|m{.19\textwidth}|}{\centering{\textbf{Type}}} &
\multicolumn{1}{m{.22\textwidth}|}{\centering{\textbf{Specification}}} &
\multicolumn{1}{m{.13\textwidth}|}{\centering{\textbf{Example}}} &
\multicolumn{1}{m{.28\textwidth}|}{\centering\arraybackslash{\textbf{Epistemic consequence(s)}}}\\\hline
monotomous\footnotemark

(one-to-none)
 &
focuses on a single group, no comparison to other groups is implied &
Catholics don't eat meat on Fridays.\vspace*{.5\baselineskip} &
We assume to know the trait prevalence/intensity in the group.\vspace*{.5\baselineskip}\\\hline
dichotomous

(one-to-one) &
there are two relevant groups, one is compared to the other\vspace*{1.5\baselineskip} &
Women are more law-abiding than men. &
We assume to know the relative prevalence/intensity of the trait in both groups.\vspace*{1.5\baselineskip} \\\hline
polytomous

(one-to-many) &
there are many relevant groups, one is singled out for inspection\vspace*{5.5\baselineskip} &
Poles make brave soldiers.\vspace*{6.5\baselineskip} &
We assume to know that the prevalence/intensity of the trait in the focal group is above average.

We don't necessarily assume to know anything about any other group in particular. \\\hline
incremental &
groups are implicitly defined and ordered by intensity of certain characteristic &
The older, the more clumsy.\vspace*{1.5\baselineskip} &
We assume to know that prevalence/intensity of the trait is monotonously linked to the group-defining metric.\\\hline

@@

\begin{flushleft}
\begin{enumerate}[label=\Alph*)]
\item
  \(\mu_{T} = 2.00\) and \(\sigma_{T} = 0.75\), with the corresponding
  \(p\left( X_{T} > X_{R} \right) = 0.945\);
\item
  \(\mu_{T} = 1.00\) and \(\sigma_{T} = 1.00\), with the corresponding
  \(p\left( X_{T} > X_{R} \right) = 0.760\);
\item
  \(\mu_{T} = 0.25\) and \(\sigma_{T} = 1.50\), with the corresponding
  \(p\left( X_{T} > X_{R} \right) = 0.555\).
\end{enumerate}
\end{flushleft}
In A, the stereotype could be considered to be very accurate as it would produce mistakes when judging individuals only 5.5\% of the time. In C, it is barely acceptable, with failure rate at 44.5\%. What about B? With the error rate at 24\% it seems quite unreliable. But before discarding it as a far-fetched overgeneralization, one should recognize that according to a popular metric proposed by Cohen
%\label{ref:RNDI9cG7tk2qD}(Cohen, 1988),
\parencite*[][]{cohen_statistical_1988}, %
 this stereotype signifies a definitely large effect size. With Cohen's \textit{d} equal to 1, it is the kind of effect that any social scientist would be more than happy to find in his or her study. Moreover, let us bear in mind that for ``new areas of research inquiry,'' effect sizes of 0.2 would not be utterly uninteresting 
%\label{ref:RNDDeitIcl8zR}(Cohen, 1988, p.25).
\parencite[][p.25]{cohen_statistical_1988}. %
 And it is just the effect size of a stereotypic difference depicted by C. Why should we then subject stereotypes to higher standards of truth than scientific findings?

@@

\setlength{\tabcolsep}{2pt}
\begin{figure}[H]
	\begin{small}
   \begin{supertabular}{m{.32\textwidth}m{.32\textwidth}m{.32\textwidth}}
   \begin{center}
   \textbf{moderate effect size}
   \end{center} &
   \begin{center}
   \textbf{large effect size}
   \end{center} &
   \begin{center}
   \textbf{very large effect size}
   \end{center} \\
	\vskip-.3in$$\mu_{T} - \mu_{R} = 0.5$$\vskip-.3in &
    \vskip-.3in$$\mu_{T} - \mu_{R} = 1.0$$\vskip-.3in &
    \vskip-.3in$$\mu_{T} - \mu_{R} = 1.5$$\vskip-.3in \\
   \includegraphics[width=\linewidth]{ART_Czarnik/Czarnik-img016.jpg} &
   \includegraphics[width=\linewidth]{ART_Czarnik/Czarnik-img017.jpg} &
   \includegraphics[width=\linewidth]{ART_Czarnik/Czarnik-img018.jpg} \\
   \end{supertabular}
   \end{small}
\caption{The effect of categorization on the observed
probabilities of \(X_{T} > X_{R}\), \(X_{T} = X_{R}\), and
\(X_{T} < X_{R}\) for three different effect sizes (all underlying
distributions are normal with \(\sigma_{T} = \sigma_{R} = 1\)).}\label{fig2-czar}
\end{figure}
When analyzing the accuracy of stereotypes regarding traits measured on
scales with a limited number of categories it is thus advisable to
consider all three possible options: \(X_{T} > X_{R}\),
\(X_{T} = X_{R}\), and \(X_{T} < X_{R}\)\footnote{The effect of categorization cannot be held constant by using the contrast between $p(X_T>X_R)$ and $p(X_T<X_R)$ as a measure. The difference $p(X_T>X_R)-p(X_T<X_R)$ tends to decrease, and the ratio $p(X_T>X_R)\ /\ p(X_T<X_R)$ tends to increase as the number of categories becomes smaller and smaller.}, as it may well turn out that
\(p\left( X_{T} = X_{R} \right)\) is far from negligible.
\enlargethispage{1\baselineskip}

\section{A few empirical examples of assessing the accuracy of sex stereotypes}
Both actual differences between the sexes and associated beliefs about these differences were intensively studied
%\label{ref:RND1zeV4PeuSF}(Williams and Best, 1982, 1990; Costa, Terracciano and McCrae, 2001; Biernat and Deaux, 2000; Buss, 2003; Pinker, 2003).
\parencites[][]{williams_measuring_1982}[][]{williams_sex_1990}[][]{costa_gender_2001}[][]{borgatta_sex_2000}[][]{buss_evolution_2003}[][]{pinker_blank_2003}. %
 In the following, I~will examine a number of possible sex stereotypes, testing their accuracy against the survey data from Polish General Social Survey 
%\label{ref:RNDDqAxDLuyEC}(Cichomski, Jerzyński and Zieliński., 2013)
\parencite[][]{cichomski_polskie_2013} %
 and the Study of Human Capital in Poland 
%\label{ref:RNDLH293GzyiT}(Górniak et al., 2015, 2019).
\parencites[][]{gorniak_bilans_2015}[][]{gorniak_bilans_2019}.%
\footnote{Representative surveys provide us with proper criteria for assessing stereotypes' accuracy. } It is irrelevant here whether most people (or any people, for that matter) subscribe to these particular stereotypes, although certainly some of the inspected traits are popularly held to be gender-differentiating (e.g. body height, earnings, interest in fashion or technology).

For each trait, probabilities of a randomly selected woman being at a
higher, the same, or lower level on the trait as compared to a randomly
selected man were computed, using the following formulae, where \emph{v}
stands for a value of the trait variable\footnote{It may be noted that a
  difference between the ``mirror-image'' probabilities, i.e.
  \(p\left( X_{F} > X_{M} \right) - p\left( X_{F} < X_{M} \right)\),
  is equal in value to asymmetric Somer's \textit{d} rank correlation coefficient
  \parencite{somers_new_1962}, when predictions are based on subjects' sex.}:
\[p\left( X_{F} > X_{M} \right) = \sum_{v = min}^{\max}{p\left( X_{F} = v \right) \cdot p\left( X_{M} < v \right)}\]

\[p\left( X_{F} = X_{M} \right) = \sum_{v = min}^{\max}{p\left( X_{F} = v \right) \cdot p\left( X_{M} = v \right)}\]

\[p\left( X_{F} < X_{M} \right) = \sum_{v = min}^{\max}{p\left( X_{F} = v \right) \cdot p\left( X_{M} > v \right)}\]

@@

\begin{figure}[H]
	\centering
   \includegraphics[width=\textwidth]{ART_Czarnik/Czarnik-img019.jpg}
\caption{Probabilistic assessment of stereotypical sex differences concerning body structure.\\
{\footnotesize Own computation from Polish General Social Survey data elicited by open-ended questions
``What is your height and weight, approximately?''}. 
}\label{fig3-czar}
\end{figure}

@@

\begin{figure}[H]
	\centering
   \includegraphics[width=\textwidth]{ART_Czarnik/Czarnik-img020.jpg}
\caption{Probabilistic assessment of stereotypical sex differences concerning pay.\\
{\footnotesize Own computation from the Study of Human Capital in Poland data elicited by open-ended questions with supplementary categorization (analysis restricted to employees with job contracts working full-time within last month, excluding self-employed).  }
}\label{fig4-czar}
\end{figure}

@@

\begin{figure}[H]
	\centering
   \includegraphics[width=\textwidth]{ART_Czarnik/Czarnik-img021.jpg}
\caption{Probabilistic assessment of stereotypical sex differences concerning interest in the mass media content.\\
{\footnotesize Own computation from Polish General Social Survey data (2002). Interest was measured on a 4-point scale: 1 not at all /2 not much /3 quite a bit /4
very much.}
}\label{fig5-czar}
\end{figure}

@@

\begin{figure}[h]
	\centering
   \includegraphics[width=\textwidth]{ART_Czarnik/Czarnik-img022.jpg}
\caption{Probabilistic assessment of stereotypical sex differences concerning skill self-evaluation.\\
{\footnotesize Own computation from the Study of Human Capital in Poland data (2017). Skill level was self-evaluated on a 5-point scale: 1 low /2 basic /3 medium /4 high /5 very high.}}\label{fig6-czar}
\end{figure}

@@

\myquote{
Imagine that you enter an elevator in a large shopping mall and two random persons—one man and one woman—unacquainted to you and to each other,\footnote{It is important to exclude the possibility that a man and a woman are a couple, so that subjects' judgment about general differences would not be contaminated by their beliefs about relative height of mated individuals. } enter after you. How likely it is that: (1) the man will be the taller of the two, (2) the woman will be the taller of the two, (3) they will be of equal height (with precision of, say, 1 cm). Make sure that probabilities add to 100\%.\footnote{It is a subject for some experimentation to find out how this task could be facilitated by a particular method of registering the probabilities (e.g. by a visual representation of probabilities on screen). }
}

### 2020-09-08 ART_Dada_Piech/Dada-PU.tex
Authors' and editorial corrections added

It was Tymoczko who attempted a certain characterisation which consisted in enumerating some tendencies, not necessarily common to all the representatives of the ``new'' philosophy of mathematics. Amongst the manifestations of the ``new'' philosophy pointed out by Tymoczko, he mentions: focusing attention on informal proofs in mathematics and on explanation which is juxtaposed with formal proofs, the use of computers to prove mathematical theorems, the issues concerned with errors in mathematics, drawing attention to the history of mathematics, and in particular to the reconstruction of essential discoveries, addressing the issue of communication within the community of mathematicians.\footnote{,,If we look at mathematics without prejudice, many features will stand out as relevant that were ignored by the foundationalist: informal proofs, historical development, the possibility of mathematical error, mathematical explanations (in contrast to proofs), communication among mathematicians, the use of computers in modern mathematics, and many more''
%\label{ref:RNDYOKoeMEYyv}(Tymoczko, 1986, p.xvi).
\parencite[][p.xvi]{tymoczko_introduction_1986}.%
}

@@

Firstly, it is about fallibility of mathematical theorems
%\label{ref:RNDEwhe4aJ9qw}(Lakatos, 1976, p.139).
\parencite[][p.139]{lakatos_proofs_1976}.%
\footnote{,,In fact Lakatos's \textit{quasi}-empiricism consists in the fallibility thesis. Although their subject matter is different, mathematical theories and empirical theories have in common the fact that they are fallible'' 
%\label{ref:RNDUrfHOQp6DB}(Koetsier, 1991, p.4).
\parencite[][p.4]{koetsier_lakatos_1991}.%
} Because since Popper attention has been paid to fallibility of statements advanced by empirical sciences, Lakatos' proposition about the fallibility of mathematical theorems is the first reason for choosing a name for the new direction in the philosophy of mathematics. Obviously, during the checking and testing stage, before they are provided with a correct ``Hilbertian'' proof, mathematical theorems are fallible.

@@

Therefore, as already stated, even though the threads of the ``new'' philosophy were invariably present in the history of deliberation on mathematics, for more than half a century, until Lakatos' publications, they were ``muffled'' by philosophy confederated with the study of the foundations\footnote{It must be emphasised, once again, that the ``Creative Mathematician'' relying on intuition and imagination has never been out of interest for the philosophy of mathematics. This aspect of considering mathematics was represented by Husserl, and under his influence by the French school of philosophy of mathematics---starting from Poincaré. Husserl's phenomenology (intuition) was invoked in Gödel's attempt to explain the ``perception'' of the objective infinite hierarchy of infinite sets. However, none of them stressed as strongly the fallibility of the theorems of the mathematics as Bôcher and Lakatos did. Since the thesis of the fallibility of mathematical theorems is the essence of Lakatos' \textit{quasi}-empiricism, the roots of \textit{quasi}-empiricism are to be found in Bôcher.}.

@@

It needs to be noted that Bôcher does not go on to belabour the comparison between a mathematician and an artist. But it appears that further conclusions with regard to the ``creative'' mathematician might be drawn from this comparison. Bôcher merely remarks that such a perception of the ``creative'' mathematician essentially allows for introduction of the notion of value among the instruments for evaluating mathematical achievements, just like it is done when evaluating a work of art.\footnote{,,Other qualities of a far more subtle sort, chief among which in both cases is imagination, go to the making of the good artist or good mathematician. I must content myself by merely recalling to you this somewhat vague and difficult though interesting field of speculation which arises when we attempt to attach \textit{value} to mathematical work, a field which is familiar enough to us all in the analogous case of artistic or literary criticism''
%\label{ref:RNDp1pZGnaAyW}(Bôcher, 1904, p.133).
\parencite[][p.133]{bocher_fundamental_1904}.%
} He himself speaks about a ``good mathematician'' in the sense in which one speaks about a ``good artist.''

@@

As he goes on describing an alternative way of reflection on mathematics, which is different from the perception of mathematics from the perspective of the ``so-called foundations,'' Bôcher notes the role of intuition among the instruments used by a ``creative'' mathematician. But here his remarks are only sketchy. As a matter of fact, he only singles out geometric, mechanical and physical intuition, saying that the significance of intuition among the instruments used by a creative mathematician is so popularly known that a mere mention of it is enough.\footnote{,,A discussion and analysis of the non-deductive methods which the creative mathematician really uses would be both interesting and instructive. Here I must content myself with the enumeration of a few of them. First and foremost, there is the use of intuition, whether geometric, mechanical, or physical. The great service which this method has rendered and is still rendering to mathematics both pure and applied is so well known that a mere mention is sufficient''
%\label{ref:RND4OfAwXmUjB}(Bôcher, 1904, p.134).
\parencite[][p.134]{bocher_fundamental_1904}.%
}

@@

Bôcher stresses that he means above all experiments in number theory (as well as in analysis). He says that experiment records---which, as one might believe, corroborate some statements (hypotheses) in number theory---often used to be contained in mathematicians' publications. He goes on to add that the fact that in his times the practice of publishing the records of such activities was abandoned does not change, in his opinion, the fact that an arithmetical experiment---one might add: in the context of mathematical discovery (to be more precise: of a number-theory character), in study practice---was as common as before.\footnote{,,Then there is the method of experiment; not merely the physical experiments of the laboratory or the geometric experiments I had occasion to speak of a few minutes ago, but also arithmetical experiments, numerous examples of which are found in the theory of numbers and in analysis. The mathematicians of the past frequently used this method in their printed works. That this is now seldom done must not be taken to indicate that the method itself is not used as much as ever''
%\label{ref:RNDQdKDMpRbg8}(Bôcher, 1904, p.134).
\parencite[][p.134]{bocher_fundamental_1904}.%
}

>>>>

It was Tymoczko who attempted a certain characterisation which consisted in enumerating some tendencies, not necessarily common to all the representatives of the ``new'' philosophy of mathematics. Amongst the manifestations of the ``new'' philosophy pointed out by Tymoczko, he mentions: focusing attention on informal proofs in mathematics and on explanation which is juxtaposed with formal proofs, the use of computers to prove mathematical theorems, the issues concerned with errors in mathematics, drawing attention to the history of mathematics, and in particular to the reconstruction of essential discoveries, addressing the issue of communication within the community of mathematicians.\footnote{``If we look at mathematics without prejudice, many features will stand out as relevant that were ignored by the foundationalist: informal proofs, historical development, the possibility of mathematical error, mathematical explanations (in contrast to proofs), communication among mathematicians, the use of computers in modern mathematics, and many more''
%\label{ref:RNDYOKoeMEYyv}(Tymoczko, 1986, p.xvi).
\parencite[][p.xvi]{tymoczko_introduction_1986}.%
}

@@

Firstly, it is about fallibility of mathematical theorems
%\label{ref:RNDEwhe4aJ9qw}(Lakatos, 1976, p.139).
\parencite[][p.139]{lakatos_proofs_1976}.%
\footnote{``In fact Lakatos's \textit{quasi}-empiricism consists in the fallibility thesis. Although their subject matter is different, mathematical theories and empirical theories have in common the fact that they are fallible'' 
%\label{ref:RNDUrfHOQp6DB}(Koetsier, 1991, p.4).
\parencite[][p.4]{koetsier_lakatos_1991}.%
} Because since Popper attention has been paid to fallibility of statements advanced by empirical sciences, Lakatos' proposition about the fallibility of mathematical theorems is the first reason for choosing a name for the new direction in the philosophy of mathematics. Obviously, during the checking and testing stage, before they are provided with a correct ``Hilbertian'' proof, mathematical theorems are fallible.

@@

Therefore, as already stated, even though the threads of the ``new'' philosophy were invariably present in the history of deliberation on mathematics, for more than half a century, until Lakatos' publications, they were ``muffled'' by philosophy confederated with the study of the foundations.\footnote{It must be emphasised, once again, that the ``Creative Mathematician'' relying on intuition and imagination has never been out of interest for the philosophy of mathematics. This aspect of considering mathematics was represented by Husserl, and under his influence by the French school of philosophy of mathematics---starting from Poincaré. Husserl's phenomenology (intuition) was invoked in Gödel's attempt to explain the ``perception'' of the objective infinite hierarchy of infinite sets. However, none of them stressed as strongly the fallibility of the theorems of the mathematics as Bôcher and Lakatos did. Since the thesis of the fallibility of mathematical theorems is the essence of Lakatos' \textit{quasi}-empiricism, the roots of \textit{quasi}-empiricism are to be found in Bôcher.}

@@

It needs to be noted that Bôcher does not go on to belabour the comparison between a mathematician and an artist. But it appears that further conclusions with regard to the ``creative'' mathematician might be drawn from this comparison. Bôcher merely remarks that such a perception of the ``creative'' mathematician essentially allows for introduction of the notion of value among the instruments for evaluating mathematical achievements, just like it is done when evaluating a work of art.\footnote{``Other qualities of a far more subtle sort, chief among which in both cases is imagination, go to the making of the good artist or good mathematician. I must content myself by merely recalling to you this somewhat vague and difficult though interesting field of speculation which arises when we attempt to attach \textit{value} to mathematical work, a field which is familiar enough to us all in the analogous case of artistic or literary criticism''
%\label{ref:RNDp1pZGnaAyW}(Bôcher, 1904, p.133).
\parencite[][p.133]{bocher_fundamental_1904}.%
} He himself speaks about a ``good mathematician'' in the sense in which one speaks about a ``good artist.''

@@

As he goes on describing an alternative way of reflection on mathematics, which is different from the perception of mathematics from the perspective of the ``so-called foundations,'' Bôcher notes the role of intuition among the instruments used by a ``creative'' mathematician. But here his remarks are only sketchy. As a matter of fact, he only singles out geometric, mechanical and physical intuition, saying that the significance of intuition among the instruments used by a creative mathematician is so popularly known that a mere mention of it is enough.\footnote{``A discussion and analysis of the non-deductive methods which the creative mathematician really uses would be both interesting and instructive. Here I must content myself with the enumeration of a few of them. First and foremost, there is the use of intuition, whether geometric, mechanical, or physical. The great service which this method has rendered and is still rendering to mathematics both pure and applied is so well known that a mere mention is sufficient''
%\label{ref:RND4OfAwXmUjB}(Bôcher, 1904, p.134).
\parencite[][p.134]{bocher_fundamental_1904}.%
}

@@

Bôcher stresses that he means above all experiments in number theory (as well as in analysis). He says that experiment records---which, as one might believe, corroborate some statements (hypotheses) in number theory---often used to be contained in mathematicians' publications. He goes on to add that the fact that in his times the practice of publishing the records of such activities was abandoned does not change, in his opinion, the fact that an arithmetical experiment---one might add: in the context of mathematical discovery (to be more precise: of a number-theory character), in study practice---was as common as before.\footnote{``Then there is the method of experiment; not merely the physical experiments of the laboratory or the geometric experiments I had occasion to speak of a few minutes ago, but also arithmetical experiments, numerous examples of which are found in the theory of numbers and in analysis. The mathematicians of the past frequently used this method in their printed works. That this is now seldom done must not be taken to indicate that the method itself is not used as much as ever''
%\label{ref:RNDQdKDMpRbg8}(Bôcher, 1904, p.134).
\parencite[][p.134]{bocher_fundamental_1904}.%
}
